---
title: "Clickbank Data Analytics"
author: "Jens Laufer"
date: "30 10 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r}
library(glue)
library(XML)
library(methods)
library(jsonlite)
library(DT)
library(ggthemes)
library(devtools)
library(ggrepel)
library(tidyverse)
library(ggbiplot)
```



```{r}
url <-
  "https://accounts.clickbank.com/feeds/marketplace_feed_v2.xml.zip"
target.dir <- tempdir()
target.file <- "{target.dir}/clickbank.zip" %>% glue()
xml.file.name <- "{target.dir}/marketplace_feed_v2.xml" %>% glue()

if (!file.exists(target.file)) {
  download.file(url,
                target.file)
  unzip(target.file, exdir = target.dir)
}

numeric.cols <-  c(
  "Gravity",
  "PercentPerSale",
  "PercentPerRebill",
  "AverageEarningsPerSale",
  "InitialEarningsPerSale",
  "TotalRebillAmt",
  "Referred",
  "Commission"
)
data <-
  xmlToDataFrame(nodes = getNodeSet(
    xmlParse(file = xml.file.name, encoding = "ISO-8859-1"),
    "//Site"
  )) %>%
  mutate(
    PopularityRank = as.integer(as.character(PopularityRank)),
    PopularityRank_bin = cut(
      PopularityRank,
      breaks = quantile(PopularityRank, probs =
                          seq(0, 1, 0.2)),
      include.lowest = T
    ),
    ActivateDate = as.Date(ActivateDate),
    HasRecurringProducts = if_else(HasRecurringProducts == 'true', T, F)
  ) %>%
  mutate_at(numeric.cols, as.double) %>% #
  mutate_at(numeric.cols, .funs = list(bin =  ~ cut(
    ., breaks = unique(quantile(
      ., probs = seq(0, 1, by = 0.20), na.rm = T
    ),), include.lowest = T
  ))) %>%
  group_by(Id) %>%
  arrange(Id, PopularityRank) %>%
  slice(1) %>%
  ungroup() 


data.pca <- data %>%
  dplyr::select(numeric.cols) %>%
  prcomp(center = T, scale. = T)

data <- data %>% bind_cols(data.pca$x %>% as_tibble())
```



PopularityRank


__Gravity__

Gravity is the number of different affiliates that are currently making sales of any given product.

Gravity helps you to find products, that already proving themselves.

You ideally look for products with at least 6.

High Gravity means high success rate, but also high competition.


__PercentPerSale__

The Percentage of Profits You Get from Each Customer

__PercentPerRebill__

__AverageEarningsPerSale__

The Average Amount Affiliates Make Per Customer Over Time

__InitialEarningsPerSale__

The Amount You'll Make Straight Away from a Single Sale.

__TotalRebillAmt__

The Average Amount People Spend After Their Initial Purchases (if They Buy More)

__Referred__

__Commission__


## Univariate Data Analysis



```{r fig.height=10, fig.width=20}
data %>%  
  select(PopularityRank, PopularityRank_bin) %>% 
  group_by(PopularityRank_bin) %>% 
  dplyr::summarise(n=n()) %>% 
  ggplot() +
  geom_bar(aes(PopularityRank_bin, n), stat='identity')
```

```{r}
data %>%
  group_by(HasRecurringProducts) %>% 
  dplyr::summarise(n=n()) %>% 
  ggplot() +
  geom_bar(aes(x=HasRecurringProducts, y=n), stat = 'identity')
  
```



```{r fig.height=10, fig.width=20}
data %>% 
  dplyr::select(contains('_bin')) %>% 
  gather(key = "var", value = "val") %>% 
  group_by(var, val) %>% 
  dplyr::summarise(n=n()) %>% 
  ggplot() +
  geom_bar(aes(val, n), stat='identity') +
  facet_wrap(~var, scales = "free")
```



```{r fig.height=20, fig.width=20}
data %>% 
  dplyr::select(numeric.cols) %>%
  gather(
    key = "var",
    value = "val"
  ) %>%
  ggplot(aes(x = '', y=val)) +
  geom_boxplot() +
  geom_jitter(alpha=0.2, color='orange')+
  facet_wrap( ~ var, scales = "free")
```


## Bivariate Data Analysis


```{r}
cor.matrix <- cor(
  data %>% dplyr::select(numeric.cols)
) 

features.corr <- cor.matrix %>% 
  as_tibble(rownames = "source") %>% 
  gather(-source, key = "target", value = "corr") %>%
  filter(source != target) %>% 
  group_by(corr) %>% 
  slice(1) %>% 
  ungroup() %>% 
  filter(corr < 0.3) %>% 
  arrange(corr) 

features <- c(features.corr %>% pull(source), features.corr %>% pull(target)) %>% unique()

```
```{r}
cor.matrix %>% corrplot::corrplot()
```

```{r fig.height=20, fig.width=20}
data %>% 
  na.omit %>% 
  ggplot()+
  geom_jitter(aes(x=Gravity, y=PercentPerSale, color=HasRecurringProducts), alpha=0.4) +
  scale_color_tableau() +
  facet_wrap(~AverageEarningsPerSale_bin~InitialEarningsPerSale_bin)+
  coord_flip()
```

```{r}
data %>% 
  filter(AverageEarningsPerSale > 100 & Gravity > 30) %>% 
  ggplot(aes(x=Gravity, y=AverageEarningsPerSale)) +
  scale_color_continuous_tableau()+
  geom_bin2d(bins=5)
```
```{r}

```








